## Variable Selection and Cleaning
### Manual Selection Based on Experience
1. Export raw data
2. Extract variable names and labels from raw data, add inclusion status and notes, export as CSV
3. Export each type of data table to a separate worksheet
4. Manually select needed variables (mainly based on clinical significance and measurability)
    - Calculate income individually, assets by household
    - Further consider the meaning of brackets
    - Double-check all "yes" responses
    - Add notes to variable list, marking variable categories
    - Exclude variables with no observations
5. Export the filtered data
6. Clean original data based on manually selected variable names, remove unnecessary variables, retain intrinsic capacity-related variables

### Independent Variable Calculation
1. Calculate final scores for each indicator based on included items (carefully consider the meaning of NA and non-empty 0 values)
2. Rename calculated independent variables

### Missing Value Variable Screening
1. Delete variables if missing values exceed 20%
   
### Algorithm Selection
1. Use Boruta method for algorithm selection

### Continuous Variable Processing
- Standardization
- Scaling and centering

### Categorical Variable Processing
- Convert to continuous variables
- Convert to dummy variables
- Label encoding (suitable for ordinal variables)

## Model Selection
1. Multiple linear regression
2. Decision trees
3. Random forests
4. Neural networks
5. Support vector machines

## Model Building
- Data resampling

## Model Validation
- 
# Code
## Install and Load Required Packages
```{r Install and Load Required Packages}
# Install and load required packages
if (!requireNamespace("haven", quietly = TRUE)) install.packages("haven")
if (!requireNamespace("dplyr", quietly = TRUE)) install.packages("dplyr") 
if (!requireNamespace("ggplot2", quietly = TRUE)) install.packages("ggplot2")
if (!requireNamespace("openxlsx", quietly = TRUE)) install.packages("openxlsx")
if (!requireNamespace("arrow", quietly = TRUE)) install.packages("arrow")
if (!requireNamespace("Boruta", quietly = TRUE)) install.packages("Boruta")
if (!requireNamespace("mice", quietly = TRUE)) install.packages("mice")

library(haven)
library(dplyr)
library(ggplot2)
library(openxlsx)
library(arrow)
library(Boruta)
library(mice)
```
## Read and Merge Data
```{r Read and Merge Data}
files <- list.files("data_raw/2015/self", pattern = "\\.dta$", full.names = TRUE)
data_list <- lapply(files, read_dta)
my_data_raw <- Reduce(function(x, y) {
    merged <- full_join(x, y, by = "ID", suffix = c("", ".dup"))
    dups <- grep("\\.dup$", names(merged), value = TRUE)
    merged <- merged %>% select(-all_of(dups))
    merged
}, data_list)
# Export as parquet format
write_parquet(my_data_raw, "data_export/my_data_raw.parquet")
```
## Variable Renaming
```{r Variable Renaming}
# Variable renaming
my_data_rename <- my_data_raw %>%
    rename(
        # Basic information renaming
        id_birth_year = ba004_w3_1,   # ID birth year
        actual_birth_year = ba002_1,  # Actual birth year 
        death = died,                 # Death status
        gender = ba000_w2_3,          # Gender

        # Intrinsic capacity physical dimension renaming
        balance_test_affected = pd001,  # Whether balance test was affected
        understand_and_willing_semi_tandem = pd002,  # Whether understands and willing to do semi-tandem stand test
        stand_test_semi_tandem_reason_1 = qd001s1,  # First reason for not completing semi-tandem stand test
        stand_test_semi_tandem_reason_2 = qd001s2,  # Second reason for not completing semi-tandem stand test
        stand_test_semi_tandem_reason_3 = qd001s3,  # Third reason for not completing semi-tandem stand test
        stand_test_semi_tandem_reason_4 = qd001s4,  # Fourth reason for not completing semi-tandem stand test
        stand_test_semi_tandem_reason_5 = qd001s5,  # Fifth reason for not completing semi-tandem stand test
        stand_test_semi_tandem_reason_6 = qd001s6,  # Sixth reason for not completing semi-tandem stand test
        stand_test_semi_tandem_reason_7 = qd001s7,  # Seventh reason for not completing semi-tandem stand test
        stand_test_semi_tandem_reason_8 = qd001s8,  # Eighth reason for not completing semi-tandem stand test
        stand_test_semi_tandem_reason_other = qd001s97,  # Other reason for not completing semi-tandem stand test
        stand_test_semi_tandem = qd002,  # Whether completed semi-tandem stand test

        understand_and_willing_tandem = pe002,  # Whether understands and willing to do tandem stand test
        stand_test_tandem_reason_1 = qe001s1,  # First reason for not completing tandem stand test
        stand_test_tandem_reason_2 = qe001s2,  # Second reason for not completing tandem stand test
        stand_test_tandem_reason_3 = qe001s3,  # Third reason for not completing tandem stand test
        stand_test_tandem_reason_4 = qe001s4,  # Fourth reason for not completing tandem stand test
        stand_test_tandem_reason_5 = qe001s5,  # Fifth reason for not completing tandem stand test
        stand_test_tandem_reason_6 = qe001s6,  # Sixth reason for not completing tandem stand test
        stand_test_tandem_reason_7 = qe001s7,  # Seventh reason for not completing tandem stand test
        stand_test_tandem_reason_8 = qe001s8,  # Eighth reason for not completing tandem stand test
        stand_test_tandem_reason_other = qe001s97,  # Other reason for not completing tandem stand test
        stand_test_tandem = qe002,       # Tandem stand test
        stand_test_tandem_time = qe003,  # Tandem stand test time

        understand_and_willing_feet_together = pf001,  # Whether understands and willing to do feet together stand test
        stand_test_feet_together_reason_1 = qf001s1,  # First reason for not completing feet together stand test
        stand_test_feet_together_reason_2 = qf001s2,  # Second reason for not completing feet together stand test
        stand_test_feet_together_reason_3 = qf001s3,  # Third reason for not completing feet together stand test
        stand_test_feet_together_reason_4 = qf001s4,  # Fourth reason for not completing feet together stand test
        stand_test_feet_together_reason_5 = qf001s5,  # Fifth reason for not completing feet together stand test
        stand_test_feet_together_reason_6 = qf001s6,  # Sixth reason for not completing feet together stand test
        stand_test_feet_together_reason_7 = qf001s7,  # Seventh reason for not completing feet together stand test
        stand_test_feet_together_reason_8 = qf001s8,  # Eighth reason for not completing feet together stand test
        stand_test_feet_together_reason_other = qf001s97,  # Other reason for not completing feet together stand test
        stand_test_feet_together = qf002, # Feet together stand test

        walk_test_reason_1 = qg001s1,  # First reason for not completing walk test
        walk_test_reason_2 = qg001s2,  # Second reason for not completing walk test
        walk_test_reason_3 = qg001s3,  # Third reason for not completing walk test
        walk_test_reason_4 = qg001s4,  # Fourth reason for not completing walk test
        walk_test_reason_5 = qg001s5,  # Fifth reason for not completing walk test
        walk_test_reason_6 = qg001s6,  # Sixth reason for not completing walk test
        walk_test_reason_7 = qg001s7,  # Seventh reason for not completing walk test
        walk_test_reason_8 = qg001s8,  # Eighth reason for not completing walk test
        walk_test_reason_other = qg001s97,  # Other reason for not completing walk test
        walk_time_first = qg002,       # Walk test time 1
        walk_time_second = qg003,      # Walk test time 2
        walk_test_aid = qg005,       # Walk test assistive device use

        sit_stand_test_reason_1 = qh001s1,  # First reason for not completing sit-to-stand test
        sit_stand_test_reason_2 = qh001s2,  # Second reason for not completing sit-to-stand test
        sit_stand_test_reason_3 = qh001s3,  # Third reason for not completing sit-to-stand test
        sit_stand_test_reason_4 = qh001s4,  # Fourth reason for not completing sit-to-stand test
        sit_stand_test_reason_5 = qh001s5,  # Fifth reason for not completing sit-to-stand test
        sit_stand_test_reason_6 = qh001s6,  # Sixth reason for not completing sit-to-stand test
        sit_stand_test_reason_7 = qh001s7,  # Seventh reason for not completing sit-to-stand test
        sit_stand_test_reason_8 = qh001s8,  # Eighth reason for not completing sit-to-stand test
        sit_stand_test_reason_other = qh001s97,  # Other reason for not completing sit-to-stand test
        sit_stand_test_completed = qh002,  # Whether completed sit-to-stand test
        sit_stand_test_time = qh003,  # Time to complete sit-to-stand test
        sit_stand_test_arm_use = qh007,  # Arm use during sit-to-stand test

        

        # Intrinsic capacity cognitive dimension renaming
        proxy_answer = db032,          # Whether answered by proxy
        recall_word_1 = dc006s1,       # Recall word 1
        recall_word_2 = dc006s2,       # Recall word 2
        recall_word_3 = dc006s3,       # Recall word 3
        recall_word_4 = dc006s4,       # Recall word 4
        recall_word_5 = dc006s5,       # Recall word 5
        recall_word_6 = dc006s6,       # Recall word 6
        recall_word_7 = dc006s7,       # Recall word 7
        recall_word_8 = dc006s8,       # Recall word 8
        recall_word_9 = dc006s9,       # Recall word 9
        recall_word_10 = dc006s10,     # Recall word 10
        recall_none = dc006s11,        # Whether recalled none
        recall_refused = dc006s12,     # Whether refused to recall

        recall_year = dc001s1,         # Recall year
        recall_month = dc001s2,        # Recall month
        recall_day = dc001s3,          # Recall day
        recall_weekday = dc002,        # Recall weekday
        recall_season = dc003,         # Recall season

        subtraction_test_1 = dc019,    # Subtraction test 1
        subtraction_test_2 = dc020,    # Subtraction test 2
        subtraction_test_3 = dc021,    # Subtraction test 3
        subtraction_test_4 = dc022,    # Subtraction test 4
        subtraction_test_5 = dc023,    # Subtraction test 5
        subtraction_tool_use = dc024,  # Whether used tools for calculation

        drawing_test = dc025,          # Drawing test


        # Intrinsic capacity psychological dimension renaming
        depression_scale_1 = dc009,    # Depression scale question 1
        depression_scale_2 = dc010,    # Depression scale question 2
        depression_scale_3 = dc011,    # Depression scale question 3
        depression_scale_4 = dc012,    # Depression scale question 4
        depression_scale_5 = dc013,    # Depression scale question 5
        depression_scale_6 = dc014,    # Depression scale question 6
        depression_scale_7 = dc016,    # Depression scale question 7
        depression_scale_8 = dc017,    # Depression scale question 8
        depression_scale_9 = dc018,    # Depression scale question 9
        night_sleep_time = da049,      # Night sleep time
        poor_sleep_frequency = dc015,  # Poor sleep frequency
        nap_time = da050,              # Nap time

        # Intrinsic capacity sensory dimension renaming
        wearing_glasses = da032,       # Whether wears glasses
        far_vision = da033,            # Far vision status
        near_vision = da034,           # Near vision status
        hearing_aid = da038,           # Whether uses hearing aid
        hearing_status = da039,        # Hearing status
        
        
        # Intrinsic capacity vitality dimension renaming
        grip_test_reason_1 = qc001s1,  # First reason for not completing grip test
        grip_test_reason_2 = qc001s2,  # Second reason for not completing grip test
        grip_test_reason_3 = qc001s3,  # Third reason for not completing grip test
        grip_test_reason_4 = qc001s4,  # Fourth reason for not completing grip test
        grip_test_reason_5 = qc001s5,  # Fifth reason for not completing grip test
        grip_test_reason_6 = qc001s6,  # Sixth reason for not completing grip test
        grip_test_reason_7 = qc001s7,  # Seventh reason for not completing grip test
        grip_test_reason_8 = qc001s8,  # Eighth reason for not completing grip test
        grip_test_reason_other = qc001s97,  # Other reason for not completing grip test
        left_hand_grip_1 = qc003,      # First left hand grip measurement
        right_hand_grip_1 = qc004,     # First right hand grip measurement
        left_hand_grip_2 = qc005,      # Second left hand grip measurement
        right_hand_grip_2 = qc006,     # Second right hand grip measurement

        breath_test_reason_1 = qb001s1,  # First reason for not completing breath test
        breath_test_reason_2 = qb001s2,  # Second reason for not completing breath test
        breath_test_reason_3 = qb001s3,  # Third reason for not completing breath test
        breath_test_reason_4 = qb001s4,  # Fourth reason for not completing breath test
        breath_test_reason_5 = qb001s5,  # Fifth reason for not completing breath test
        breath_test_reason_6 = qb001s6,  # Sixth reason for not completing breath test
        breath_test_reason_7 = qb001s7,  # Seventh reason for not completing breath test
        breath_test_reason_8 = qb001s8,  # Eighth reason for not completing breath test
        breath_test_reason_other = qb001s97,  # Other reason for not completing breath test
        breath_test_1 = qb002,         # First breath function test
        breath_test_2 = qb003,         # Second breath function test
        breath_test_3 = qb004,         # Third breath function test

        hemoglobin = bl_hgb          # Hemoglobin level
    )
# Export data containing all renamed columns
renamed_columns <- names(my_data_rename)
original_columns <- names(my_data_raw)
renamed_only_columns <- setdiff(renamed_columns, original_columns)
my_data_renamed_only <- my_data_rename %>%
    select(all_of(renamed_only_columns))
write.csv(my_data_renamed_only, "data_export/renamed_data.csv", row.names = FALSE)

```
## Age Data Cleaning
```{r Age Data Cleaning}
# Remove data where both actual birth year and ID birth year are missing
my_data_year_na <- my_data_rename %>%
    filter(!(is.na(actual_birth_year) & is.na(id_birth_year)))

# Calculate age
my_data_age <- my_data_year_na %>%
    mutate(age = 2015 - coalesce(actual_birth_year, id_birth_year))

# Age cleaning
my_data_elder <- my_data_age %>%
    filter(age >= 60)

# Output total number of individuals
total_individuals <- nrow(my_data_elder)
print(paste("Total number of individuals:", total_individuals))
my_data_wash <- my_data_elder

```
## Intrinsic Capacity Score Calculation
### Physical Dimension Calculation
```{r Physical Dimension Calculation}
# Calculate walk test time (correct)
my_data_wash <- my_data_wash %>%
    mutate(
        final_walk_time = case_when(
            walk_time_first == 993 & walk_time_second == 993 ~ 0,
            (is.na(walk_time_first) & is.na(walk_time_second)) | (walk_time_first == 999 & walk_time_second == 999) | (is.na(walk_time_first) & walk_time_second == 999) | (walk_time_first == 999 & is.na(walk_time_second)) ~ case_when(
                rowSums(select(., starts_with("walk_test_reason_")) == 4, na.rm = TRUE) > 0 ~ 0,
                rowSums(select(., starts_with("walk_test_reason_")) == 6, na.rm = TRUE) > 0 ~ 0,
                TRUE ~ NA_real_
            ),
            TRUE ~ case_when(
                walk_test_aid == 1 ~ if_else(2.5 / pmin(walk_time_first, walk_time_second, na.rm = TRUE) >= 1, 1, 0),
                walk_test_aid %in% c(2, 3, 4, 97) ~ 0,
                TRUE ~ NA_real_
            )
        )
    )

# Count different values of final walk time score, including NA
table(my_data_wash$final_walk_time, useNA = "always")

# Calculate balance score
# Calculate semi-tandem stand time score (correct)
my_data_wash <- my_data_wash %>%
    mutate(
        final_semi_tandem_time = case_when(
            stand_test_semi_tandem %in% c(993) ~ 0, # Because there are cases where this variable is 993 but reasons don't have 4 and 6, so directly assign 0, prioritize this variable
            stand_test_semi_tandem %in% c(999, NA) ~ case_when(
                rowSums(select(., starts_with("stand_test_semi_tandem_reason_")) == 4, na.rm = TRUE) > 0 ~ 0,
                rowSums(select(., starts_with("stand_test_semi_tandem_reason_")) == 6, na.rm = TRUE) > 0 ~ 0,
                TRUE ~ NA_real_
            ),
            stand_test_semi_tandem == 1 ~ 1,
            stand_test_semi_tandem == 5 ~ 0,
            TRUE ~ NA_real_
        )
    )


# Count different values of semi-tandem stand time score, including NA
table(my_data_wash$final_semi_tandem_time, useNA = "always")


# Calculate tandem stand time score (correct)
my_data_wash <- my_data_wash %>%
    mutate(
        final_tandem_time = case_when(
            stand_test_tandem %in% c(993) ~ 0, # Because there are cases where this variable is 993 but reasons don't have 4 and 6, so directly assign 0, prioritize this variable
            stand_test_tandem %in% c(999, NA) ~ case_when(
                rowSums(select(., starts_with("stand_test_tandem_reason_")) == 4, na.rm = TRUE) > 0 ~ 0,
                rowSums(select(., starts_with("stand_test_tandem_reason_")) == 6, na.rm = TRUE) > 0 ~ 0,
                TRUE ~ NA_real_
            ),
            stand_test_tandem == 1 ~ 1,
            stand_test_tandem == 5 ~ if_else(stand_test_tandem_time >= 10, 1, 0),
            TRUE ~ NA_real_
        )
    )
# Count different values of tandem stand score, including NA
table(my_data_wash$final_tandem_time, useNA = "always")


# Calculate feet together stand time score (correct)
my_data_wash <- my_data_wash %>%
    mutate(
        final_feet_together_time = case_when(
            stand_test_feet_together %in% c(993) ~ 0,
            stand_test_feet_together %in% c(999, NA) ~ case_when(
                rowSums(select(., starts_with("stand_test_feet_together_reason_")) == 4, na.rm = TRUE) > 0 ~ 0,
                rowSums(select(., starts_with("stand_test_feet_together_reason_")) == 6, na.rm = TRUE) > 0 ~ 0,
                TRUE ~ NA_real_
            ),
            stand_test_feet_together == 1 ~ 1,
            stand_test_feet_together == 5 ~ 0,
            TRUE ~ NA_real_
        )
    )

# Count different values of feet together stand score, including NA
table(my_data_wash$final_feet_together_time, useNA = "always")

# Calculate final balance score (correct)
my_data_wash <- my_data_wash %>%
    mutate(
        final_balance_score = case_when(
            rowSums(select(., final_semi_tandem_time, final_tandem_time, final_feet_together_time) == 1, na.rm = TRUE) >= 2 ~ 1,
            rowSums(is.na(select(., final_semi_tandem_time, final_tandem_time, final_feet_together_time))) >= 2 ~ NA_real_,
            rowSums(is.na(select(., final_semi_tandem_time, final_tandem_time, final_feet_together_time))) == 1 &
            rowSums(select(., final_semi_tandem_time, final_tandem_time, final_feet_together_time) == 1, na.rm = TRUE) == 1 &
            rowSums(select(., final_semi_tandem_time, final_tandem_time, final_feet_together_time) == 0, na.rm = TRUE) == 1 ~ NA_real_,
            TRUE ~ 0
        )
    )
# Count different values of final balance score, including NA
table(my_data_wash$final_balance_score, useNA = "always")

# Calculate sit-to-stand test time (correct)
my_data_wash <- my_data_wash %>%
    mutate(
        final_sit_stand_time = case_when(
            sit_stand_test_completed %in% c(993) ~ 0,
            sit_stand_test_completed %in% c(999, NA) ~ case_when(
                rowSums(select(., starts_with("sit_stand_test_reason_")) == 4, na.rm = TRUE) > 0 ~ 0,
                rowSums(select(., starts_with("sit_stand_test_reason_")) == 6, na.rm = TRUE) > 0 ~ 0,
                TRUE ~ NA_real_
            ),
            sit_stand_test_completed == 1 ~ case_when(
                sit_stand_test_arm_use == 1 ~ 0,
                sit_stand_test_arm_use == 5 ~ case_when( # This is where data and code say 5, but questionnaire says 1, took a while to figure out
                    sit_stand_test_time <= 12 ~ 1,
                    sit_stand_test_time > 12 ~ 0,
                    TRUE ~ NA_real_
                    ),
                TRUE ~ NA_real_ 
            ),
            sit_stand_test_completed == 5 ~ 0,
            TRUE ~ NA_real_
        )
    )

# View different values of sit-to-stand test time score, including NA
table(my_data_wash$final_sit_stand_time, useNA = "always")

# Calculate physical dimension total score (correct)
my_data_wash <- my_data_wash %>%
    mutate(
        final_physical_score = rowSums(select(., final_walk_time, final_balance_score, final_sit_stand_time), na.rm = FALSE)
    )

# View different values of physical dimension total score, including NA
table(my_data_wash$final_physical_score, useNA = "always")

# Export physical dimension variables and ID, remove all other variables, export as CSV
required_columns <- c(
    "ID", "final_walk_time", "final_semi_tandem_time", "final_tandem_time", "final_feet_together_time", "final_balance_score", "final_sit_stand_time", "final_physical_score"
)
my_data_physical <- my_data_wash %>%
    select(all_of(required_columns))

write.csv(my_data_physical, "data_export/physical_dimension_data.csv", row.names = FALSE)
```